\input{.lib/form.class.tex}
\begin{document}
\NDFormCommonHeaderImpl{IMI-1}{Visa Application Form}{签证申请表 \S{} Formulaire de demande de visa}



\begin{minipage}{\textwidth}
	\small
	\textbf{INSTRUCTIONS}:
	\inlinelistitem To apply for a visa, your passport must be politically acceptable. Otherwise you may only get a special entry permit (IMI-6).
	\inlinelistitem You may file a paper-based application only if you do not qualify electronic visa application.
	\inlinelistitem This form must be filled with American English or Simplified Chinese.
	\inlinelistitem If you plan to travel as a group with other persons (friend/family), attach an IMI-2 form.
	\inlinelistitem According to the purpose of your planned travel, attach an IMI-3 form (Domestic Tour Plan, for nonresidential purposes) or an IMI-4 form (Residing Plan, for residential purposes).
	\inlinelistitem If you have more than one valid travel document, attach an IMI-9 form (Visa Applicant Identity Statement).
	\inlinelistitem You may not have multiple visas of Neoparia Demokratia simultaneously. If a new visa is granted, the old one shall be revoked. If you already have a visa of Neoparia Demokratia, you must declare its number.
	\inlinelistitem Your full name (raw) may or may not be digitally recorded, depending on computer software capabilities.
	\inlinelistitem Fields marked with asterisk (*) are optional.
	\inlinelistitem Depending on the category applied for, required documents may vary. Consult the latest visa policy before submitting.
\end{minipage}
\vskip 10pt




\formbrickcontentheight=27pt

\textsf{\small Is an agent filling this form on behalf of the applicant? If not, leave these boxes empty.}
\par\hrule
\formbrickVlineLeft%
\makesoftformbrick{0.5\linewidth}{\formfieldlead Agent Full Name}{~}\formbrickVlineMid%
\makesoftformbrick{0.5\linewidth}{\formfieldlead Relation to the Applicant}{~}\formbrickVlineRight%
\par\hrule
\vskip 5pt

\formbrickcontentheight=33pt

\par\hrule
\formbrickVlineLeft%
\makesoftformbrick{\linewidth}{\formfieldlead Full Name (ASCII) \footnotesize (All uppercase letters.)}{~}\formbrickVlineRight%
\par\hrule
\formbrickVlineLeft%
\makesoftformbrick{\linewidth}{\formfieldlead Full Name (Raw) \footnotesize (Leave empty if same to ASCII.)}{~}\formbrickVlineRight%
\par\hrule
\formbrickVlineLeft%
\makesoftformbrick{\linewidth}{\formfieldlead Passport MRZ \footnotesize (First line only, without trailing `<' marks.)}{~}\formbrickVlineRight%
\par\hrule
\vskip 5pt

\formbrickcontentheight=27pt

\par\hrule
\formbrickVlineLeft%
\makesoftformbrick{0.33\linewidth}{\formfieldlead Nationality \footnotesize (Country code)}{~}\formbrickVlineMid%
\makesoftformbrick{0.33\linewidth}{\formfieldlead Passport No.}{~}\formbrickVlineMid%
\makesoftformbrick{0.33\linewidth}{\formfieldlead Passport Expiry Date}{~}\formbrickVlineRight%
\par\hrule
\formbrickVlineLeft%
\makesoftformbrick{0.33\linewidth}{\formfieldlead Date of Birth}{~}\formbrickVlineMid%
\makesoftformbrick{0.33\linewidth}{\formfieldlead Place of Birth \footnotesize (Country code)}{~}\formbrickVlineMid%
\makesoftformbrick{0.33\linewidth}{\formfieldlead Old Visa No. *}{~}\formbrickVlineRight%
\par\hrule
\formbrickMiniRow{\footnotesize\sffamily Date format: YYYY-MM-DD. Use the Gregorian calendar.}%
\par\hrule
\vskip 5pt

\par\hrule
\formbrickVlineLeft%
\parbox{\linewidth-6pt}{
    \leavevmode\vskip 1pt
	\sffamily
	\parbox{\linewidth-12em}{Fill black the option applicable to you.}\hfill\parbox{3em}{YES}\parbox{3em}{NO}\\
	\parbox{\linewidth-12em}{\formfieldlead\sffamily I am or was a government official.}\hfill\parbox{3em}{$\bigcirc$}\parbox{3em}{$\bigcirc$}\\
	\parbox{\linewidth-12em}{\formfieldlead\sffamily I am the leader of a group application case.}\hfill\parbox{3em}{$\bigcirc$}\parbox{3em}{$\bigcirc$}\\
	\parbox{\linewidth-12em}{\formfieldlead\sffamily I was ever admitted into Neoparia Demokratia as a foreigner.}\hfill\parbox{3em}{$\bigcirc$}\parbox{3em}{$\bigcirc$}
\vskip 4pt}\formbrickVlineRight%
\par\hrule
\vskip 5pt

\par\hrule
\formbrickVlineLeft%
\makesoftformbrick{0.25\linewidth}{\formfieldlead Category Code}{~}\formbrickVlineMid%
\makesoftformbrick{0.5\linewidth}{\formfieldlead Category Detail *}{~}\formbrickVlineMid%
\makesoftformbrick{0.25\linewidth}{\formfieldlead Intended Arrival Date}{~}\formbrickVlineRight%
\par\hrule
\formbrickMiniRow{\footnotesize\sffamily Browse the list of visa categories before filling the fields above.}%
\par\hrule
\vskip 5pt


\par\hrule
\formbrickVlineLeft%
\makesoftformbrick{\linewidth}{\formfieldlead Home Address}{~}\formbrickVlineRight%
\par\hrule
\formbrickVlineLeft%
\makesoftformbrick{0.5\linewidth}{\formfieldlead Email Address}{~}\formbrickVlineMid%
\makesoftformbrick{0.5\linewidth}{\formfieldlead TEL *}{~}\formbrickVlineRight%
\par\hrule
\vskip 5pt




\parbox{\linewidth}{
	\small
	STATEMENT OF THE APPLICANT:\par\vskip 5pt
	I hereby swear that the information provided above is accurate. I acknowledge that any error or inaccurary may lead to the denial of issuing visa or the denial of admission upon arrival, or even criminal investigation/prosecution.\par\vskip 5pt
	\bfseries
	Signature:\hfill
	Date:\hfill
	\hspace{1pt}\par
}
\vskip 15pt
\hrule
\begin{center}
	\small OFFICIAL USE ONLY
\end{center}




\end{document}
